100 Years of Social Work Research: A Data Science Perspective

### 2015-01-13 Analysis.Rmd
Updated analysis with Ebsco Complete Datafile. All currently functional.

ggsurv(survival.journals) + 
    geom_line(data = median.survival, aes(time, quant), linetype="longdash") +
    annotate("segment", x = 32, xend = 27, y = .12, yend = .12, size = .25, arrow =arrow()) +
    geom_text(x = 45, y =.12, label = "median survival", size = 4) + 
    geom_text(x = 75, y =.75, label = "+ = Last year in print", size = 4) +
    ylim(0,1) +
    xlim(0,100) + 
    xlab("Survival Time (in years)") +
    ylab("Survival Probability") +
    ggtitle("Survival Probability of Social Work Journals")

@@

select.keywords <- c("power", "oppression", "discrimination", "socialjustice", "qualitativeresearch")
select.keywords.df <- kp.year %>% filter(keyword %in% select.keywords)

@@

#write.csv(location, "location.csv")

@@

```{r location_over_time, warning=FALSE, message=FALSE, echo=FALSE}

year <- filter(pi.df, attributes == "YR") %>%
    mutate(year = as.numeric(record)) %>% select(-record, -attributes)

@@

location.year <- location.temp %>% 
         left_join(year) %>%
         group_by(country, year) %>%
         summarise(n = n()) %>%
         arrange(country, year, n)

@@

@@

ggplot(location.year.top, aes(x = year, y = n, colour = country )) + geom_line() +
    ggtitle("Number of articles by Top 5 Countries")

top.locations.no.us <- LO.df %>% 
                select(Country) %>%
                slice(2:6)

@@

ggplot(location.year.top.no.us, aes(x = year, y = n, colour = country )) + geom_line() +
    ggtitle("Number of article by Top 5 Countries (excluding United States)")
```

@@

n_authors.1t <- n_authors.1 %>% mutate(n = ifelse(n >=13, 13, n))

ggplot(n_authors.1t, aes(x=as.factor(n))) + 
    geom_bar(fill="white", colour="black") + 
    #stat_bin(binwidth=.5) +
    ggtitle("Number of Authors Listed Per Article") + 
    xlab("Author") +
    ylab("Number of Articles") +
    scale_y_continuous(limits = c(0, 15000), breaks = seq(0, 14000, 2000)) + 
    scale_x_discrete(limits = c(as.character(1:12), "13+"))

@@

plot.author.count2 <- ggplot(n_authors, aes(as.numeric(year), y=average.n, group=1)) +  
    geom_ribbon(aes(ymin = average.n-std.dev, ymax=average.n+std.dev), colour="lightblue", fill="lightblue", alpha=.40) +
    geom_line(colour="black") + 
    geom_segment(aes(x= 1940, y = 5.5, xend = 1935, yend = 5.5), 
                 arrow=arrow(length=unit(0.25, "cm"))) +
    annotate("text", x = 1951, y = 5.5, label = "1 outlier case of \n24 listed authors", size=3.5) +
    ylab("Average number of authors (black) \nStandard deviation (light blue") +
    xlab("Publication year") +
    ggtitle("Average Number of Authors per Article Over Time")

@@

#n_authors_unique <- n_authors %>% 
#        left_join(year) %>%
#        group_by(author) %>%
#        summarise(Distinct = n())

>>>>

ggsurv(survival.journals) + 
    geom_line(data = median.survival, aes(time, quant), linetype="longdash") +
    annotate("segment", x = 32, xend = 27, y = .12, yend = .12, size = .25, arrow =arrow()) +
    geom_text(x = 45, y =.12, label = "median survival", size = 4) + 
    geom_text(x = 75, y =.75, label = "+ = Last year of indexing", size = 4) +
    ylim(0,1) +
    xlim(0,100) + 
    xlab("Survival Time (in years)") +
    ylab("Survival Probability") +
    ggtitle("Survival Probability of Social Work Journals")

@@

select.keywords <- c("depression", "hiv")
select.keywords.df <- kp.year %>% filter(tolower(keyword) %in% select.keywords)

@@

#write.csv(locations, "location.csv")

@@

```{r location_over_time, warning=FALSE, message=FALSE, echo=FALSE}
library(RColorBrewer)
year <- filter(pi.df, attributes == "YR") %>%
    mutate(year = as.numeric(record)) %>% select(-record, -attributes)

@@

location.year <- location.temp %>% 
         left_join(year) %>%
         group_by(country, year) %>%
         summarise(n = n()) %>%
         arrange(country, year, n) %>%
         mutate(cumsum_n = cumsum(n), log_n = log(n+1))

@@

top.locations$Country <- gsub(" ", "", top.locations$Country)

@@

ggplot(location.year.top, aes(x = year, y = log_n, colour = country )) + 
    geom_line(size = 1.25) +
    ggtitle("Log Number of Articles by Countries With Highest Scholarly Ouput") +
    xlab("Publication Year") + 
    ylab("log N+1") +
    theme(legend.position=c(.210, .7))

top.locations.no.us <- LO.df %>% 
                select(Country) %>%
                slice(2:10)

top.locations.no.us$Country <- gsub(" ", "", top.locations.no.us$Country)

@@

ggplot(location.year.top.no.us, aes(x = year, y = cumsum_n, colour = country )) + geom_line(size=1.00) +
    ggtitle("Cumulative Number of Article by Countries with Highest Scholarly Output \n(Excluding the United States)") +
    theme(legend.position=c(.210, .6))
```

@@

n_authors.1t <- n_authors.1 %>% mutate(n = ifelse(n >=6, 6, n)) %>% 
    group_by(n) %>%
    summarise(Articles = n())

ggplot(n_authors.1t, aes(x = n, y = Articles)) +
    geom_bar(stat="identity", colour="black", fill = "white") +
    geom_text(aes(label = Articles), vjust=-.3, size = 4) +
    scale_x_discrete(limits = c(as.character(1:5), "6+")) + 
    ggtitle("Number of Articles by Author Count") + 
    xlab("Author Count") + 
    ylab("Articles")
```

@@

plot.author.count2 <- ggplot(n_authors, aes(as.numeric(year), y=average.n, group=1)) +  
    geom_ribbon(aes(ymin = average.n-std.dev, ymax=average.n+std.dev), colour="lightblue", fill="lightblue", alpha=.40) +
    geom_line(colour="black") + 
    geom_segment(aes(x= 1940, y = 5.5, xend = 1935, yend = 5.5), 
                 arrow=arrow(length=unit(0.25, "cm"))) +
    annotate("text", x = 1951, y = 5.5, label = "1 outlier case of \n24 listed authors", size=3.5) +
    ylab("Average number of authors (black) \nStandard deviation (light blue)") +
    xlab("Publication year") +
    ggtitle("Average Number of Authors per Article Over Time")

@@
